---
title: "Literature Review"
authors: "Björn Boening, Laurence Hendry, and Cody Koebnick"
date: "The 21st of October, 2015"
nocite: |
  @Beckman2002a
  @Casella2006
  @Daxecker2015
  @ElioMarchione2014
  @Granovetter1973
  @Greengard.2012
  @Grover2007
  @Hanson2010
  @Kaluza2010
  @Kiourktsoglou2012
  @Marchione2013
  @Mastrobuoni2014
  @Mejia.2009
  @Short.2008
  @Stomakhin.2011
  @Twyman-Ghoshal2014
  @Wang2013
  @Wang2013a
bibliography: 
  - library.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is the introduction section, it should give a quick idea of the topic of the literature review, such as the central theme or organizational pattern.

## Body

The body contains your discussion of sources and is organized either chronologically, thematically, or methodologically (see below for more information on each).

## Conclusions/Recommendations: 

The conclusion is where you discuss what you have drawn from reviewing literature so far. Where might the discussion proceed?

##  Extra formatting information incase we need it, bros

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

##Cited Works:

